The 2014 SMT Competition

### 2015-08-03 2014/report/SMTCOMP.tex
Minor. Local variables (for Emacs) added.

SMT-COMP 2014 successfully executed the comparison among solvers that is the main goal
of the competition. The new computational infrastructure, StarExec, worked very well for the purpose. The competition saw a renewed interest in participation\textemdash there were record numbers of teams participating, solvers entered, teams and solvers that had never before participated, benchmarks used, and amount of computation performed. Although the 2014 results are not readily comparable to previous years (because of changes in benchmarks and equipement), the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years. As a partial comparison, solvers that performed well in previous years are included in the this year's competition. However, rerunning the competition on the old hardware or on the old benchmarks was out of the scope of the organizers' task.

@@

>>>>

SMT-COMP 2014 successfully executed the comparison among solvers that is the main goal
of the competition. The new computational infrastructure, StarExec, worked very well for the purpose. The competition saw a renewed interest in participation\textemdash there were record numbers of teams participating, solvers entered, teams and solvers that had never before participated, benchmarks used, and amount of computation performed. Although the 2014 results are not readily comparable to previous years (because of changes in benchmarks and equipment), the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years. As a partial comparison, solvers that performed well in previous years are included in the this year's competition. However, rerunning the competition on the old hardware or on the old benchmarks was out of the scope of the organizers' task.

@@

%% Local Variables:
%% mode: LaTeX
%% ispell-local-dictionary: "american"
%% mode: flyspell
%% LocalWords: Tjark Uppsala
%% End:
